Fractional Types

### 2019-11-08 fracGC/p.tex
fixed bib link
reorganize paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PiFrac}

@@

@@

When ancilla bits are created they are created with a specific
value. This value is encoded in the circuit. We use a Singleton type
to remember this information. We add the following:

ETA SIG

The value of fractional type represents the ``garbage collector.''
The garbage collector is specialized to collect a single value, which
is the value used to create the ancilla value. At this point, if the
garbage collector encounters a different value, it doesn't know what
to do, and would need to throw an exception. This situation in
\verb|PiFracDyn.agda| is similar to current solutions (e.g. Quipper)
but actually more general as it allows non-scoped ancilla allocation
and de-allocation. Show examples.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Generalizing to Non-Scoped Ancilla}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Space Denotational Semantics}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{../../cites.bib}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preliminaries: Pi}

Our approach to reversible quantum programming based on type
isomorphisms. Examples.

Ancilla problem in the context of Pi using eta and epsilon 
informally.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PiFrac: Generalizing Scoped Ancilla, Runtime Check}

Formalize ancilla problem in the context of Pi using eta and epsilon
as done in PiFracDyn; more general than scoped; still runtime
check.

When ancilla bits are created they are created with a specific
value. This value is encoded in the circuit. The value of fractional
type represents the ``garbage collector.''  The garbage collector is
specialized to collect a single value, which is the value used to
create the ancilla value. At this point, if the garbage collector
encounters a different value, it doesn't know what to do, and would
need to throw an exception. This situation in \verb|PiFracDyn.agda| is
similar to current solutions (e.g. Quipper) but actually more general
as it allows non-scoped ancilla allocation and de-allocation. Show
examples.

@@

@@

We use a Singleton type
to remember this information.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Space Denotational Semantics?}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{../cites.bib}
